Target Markdown

### 2022-05-23 _targets.Rmd
whole pipeline finalized, changed the way of calculating "one_author" target to allow for faster and smoother compute

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "httr",
                            "rjson",
                            "keyring",
                            "RSQLite",
                            "DBI"
                            ))

@@

    # tar_target(one_author,
    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
 #              format = "qs"),
      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv"), nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")

@@

   tar_target(topic_model_input,
              make_topic_model_input(all_pubs),
                format = "qs") #,
   # --> fce find k 
   # tar_target(topic_model,
   #            make_topic_model(topic_model_input),
   #             format = "qs")

@@

    # tar_target(clustering,
    #            calc_clustering(graph), 
    #            format = "qs")
    # 
)

@@

    # tar_target(ind_pubs,
    #            calc_ind_pubs(one_author), 
    #            format = "qs")
    # 
)

@@

    # tar_target(ind_topics,
    #            calc_ind_topics(topic_model, two_authors), 
    #            format = "qs")

@@

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering = NULL, ind_topics = NULL, ind_pubs = NULL),
               format = "qs")

>>>>

# load libraries for make
tar_option_set(packages = c("dplyr",
                            "tidyr",
                            "purrr",
                            "readr",
                            "quanteda",
                            "igraph",
                            "DiagrammeR",
                            "tibble",
                            "stringr",
                            "topicmodels",
                            "ggplot2",
                            "scales",
                            "ldatuning",
                            "quanteda",
                            "data.table",
                            "tidytext",
                            "tm",
                            "RSQLite",
                            "DBI"
                            ))

@@

    # tar_target(one_author,
    #           read.csv2(here::here("data", "raw",    #"Binter_pubs.csv")),
 #              format = "qs"),
      tar_target(ids, read.csv2(here::here("data", "raw", "supervisors.csv"), nrows = 20),
              format = "qs"),
      tar_target(ids_complete, create_ids_complete(ids),
              format = "qs"),
    tar_target(ids_complete_vector,
               make_ids_complete_vector(ids_complete)),
    tar_target(db_path,
           here::here("data", "raw", "czech_sci_db.sqlite")),
    tar_target(all_pubs,
           get_all_pubs(db_path, ids_complete), 
              format = "qs"),
    tar_target(one_author,
           read_one_author(db_path, ids_complete_vector, ids_complete), 
              format = "qs", pattern = map(ids_complete_vector), iteration = "list")

@@

   tar_target(topic_model_input,
              make_topic_model_input(all_pubs)) #,

    # tar_target(topic_number,
    #           find_topic_number(topic_model_input),
    #             format = "qs") #, 
    # tar_target(topic_model,
    #            make_topic_model(topic_model_input),
    #             format = "qs")

@@

     tar_target(clustering,
                calc_clustering(graph, ids_complete, one_author, db_path),
               format = "qs", pattern = map(graph, one_author), iteration = "list") 
    #            
    # 
)

@@

     tar_target(ind_pubs,
                calc_ind_pubs(one_author, ids_complete, db_path), 
                format = "qs", pattern = map(one_author),                  iteration = "list")

@@

     tar_target(ind_topics,
                calc_ind_topics(topic_model = NULL, one_author, ids_complete, db_path), 
                format = "qs", pattern = map(one_author), iteration = "list")

@@

    tar_target(final_data,
               calc_final_data(eigen_centr, clustering, ind_topics, ind_pubs),
               format = "qs") #,
     # tar_target(testing,
     #           just_test(eigen_centr, clustering, ind_topics = NULL, ind_pubs = NULL),
     #           format = "qs")
